Vitaly Ford, Ambareen Siraj, Mohammad Ashiqur Rahman

\section*{$\ast$$\ast$\+Abstract$\ast$$\ast$}

The Advanced Metering Infrastructure (A\+MI) plays a critical role in the Smart Grid. In regarding the usage of smart meters in A\+MI, there is a primary concern about how utility companies manage energy consumption data, particularly with respect to consumer privacy. This research presents a novel protocol for secure and efficient communication of energy consumption data, protecting its confidentiality, integrity, and privacy while utilizing the existing Grid infrastructure. The protocol supports time-\/of-\/use billing and data mining for advanced fine-\/grained data analysis. We report on the empirical results of the theoretical, experimental, and comparative analyses of the proposed protocol.

\section*{$\ast$$\ast$\+Published$\ast$$\ast$}

\href{http://www.sciencedirect.com/science/article/pii/S0022000016300472}{\tt Journal of Computer and System Sciences} {\itshape Volume 83, Issue 1, February 2017, Pages 84–100}

Available \href{https://www.researchgate.net/publication/305077004_Secure_and_efficient_protection_of_consumer_privacy_in_Advanced_Metering_Infrastructure_supporting_fine-grained_data_analysis}{\tt here}.

{\itshape Protocol implementation by Daniel Tyler}

\section*{$\ast$$\ast$\+Implementation$\ast$$\ast$}

Doxygen comments have been added to all the source files.

Compile via {\ttfamily \$ doxygen doxygen.\+config}

Currently looking into an external host to publish the documentation on. May possibly utilize Github\textquotesingle{}s wiki functionality.

{\bfseries Depends}

\href{http://cryptopp.com/}{\tt Crypto++} version 5.\+0.\+0 or greater.

\href{https://omnetpp.org/}{\tt O\+M\+Net++} version 5.\+0 or greater. 